plantecophys - an R package for analysing and modelling leaf gas exchange data

### 2015-09-10 manuscript.Rmd
Added reference

To demonstrate a practical application of the key functions in the package, I use field-collected data from Medlyn et al. [-@medlyn2007] on *Eucalyptus delegatensis*. Both A-C~i~ curves and 'spot gas exchange' data (i.e. leaf gas exchange measurements at prevailing environmental conditions) were collected. Using the `fitacis` function, it is straightforward to fit all `r length(acifits)` curves to the A-C~i~ data, and make standard plots of the fitted curves (shown in Fig. 5a). The fitted coefficients are easily extracted, and used to plot a standard comparison of fitted V~cmax~ and J~max~ values (Fig. 5b), which show the typical correlation between the two.

@@

\
**Figure 5**. Example application of the plantecophys package to A-C~i~ curves and spot gas exchange measurements on *Eucalyptus delegatensis*. (a) Fitted A-C~i~ curves with one curve highlighted (b) Estimates of J~max~ plotted against V~cmax~, obtained from the fitted curves in panel (a). Solid line is a regression line (J~max~ = `r round(lmjvt$estimate[1],2)` + `r signif(lmjvt$estimate[2],2)` V~cmax~, R^2^ = `r signif(lmjvg$r.squared,2)`) with a 95% confidence interval for the mean. (c) Modelled (with the model of Medlyn et al. 2011) versus measured g~s~ (p `r pval(lmgpredg$p.value)`, R^2^ = `r signif(lmgpredg$r.squared,2)`). Measurements included a wide range of environmental conditions (PAR, T~leaf~, D). In this example, only g~1~ was fit (estimate = `r signif(g1,3)`, 95% CI = `r paste(signif(g1ci,3), collapse=" - ")`). (d) The predicted response of ITE (A~n~ / E) as a function of D from the fitted model in panel (c) (solid line), and the measurements from panel (c) when PAR > 1000.

>>>>

To demonstrate a practical application of the key functions in the package, I use field-collected data from Medlyn et al. [-@medlyn2007, @medlynfigshare] on *Eucalyptus delegatensis*. Both A-C~i~ curves and 'spot gas exchange' data (i.e. leaf gas exchange measurements at prevailing environmental conditions) were collected. Using the `fitacis` function, it is straightforward to fit all `r length(acifits)` curves to the A-C~i~ data, and make standard plots of the fitted curves (shown in Fig. 5a). The fitted coefficients are easily extracted, and used to plot a standard comparison of fitted V~cmax~ and J~max~ values (Fig. 5b), which show the typical correlation between the two.

@@

\
**Figure 5**. Example application of the plantecophys package to A-C~i~ curves and spot gas exchange measurements on *Eucalyptus delegatensis* (data can be downloaded from [@medlynfigshare]) (a) Fitted A-C~i~ curves with one curve highlighted (b) Estimates of J~max~ plotted against V~cmax~, obtained from the fitted curves in panel (a). Solid line is a regression line (J~max~ = `r round(lmjvt$estimate[1],2)` + `r signif(lmjvt$estimate[2],2)` V~cmax~, R^2^ = `r signif(lmjvg$r.squared,2)`) with a 95% confidence interval for the mean. (c) Modelled (with the model of Medlyn et al. 2011) versus measured g~s~ (p `r pval(lmgpredg$p.value)`, R^2^ = `r signif(lmgpredg$r.squared,2)`). Measurements included a wide range of environmental conditions (PAR, T~leaf~, D). In this example, only g~1~ was fit (estimate = `r signif(g1,3)`, 95% CI = `r paste(signif(g1ci,3), collapse=" - ")`). (d) The predicted response of ITE (A~n~ / E) as a function of D from the fitted model in panel (c) (solid line), and the measurements from panel (c) when PAR > 1000.
